---
title: "bandit-json"
author: "mht"
date: "March 15, 2015"
output: html_document
---

We are analyzing the data slightly differently due to a different interface with Mechnical Turk. The code below reads in individual subject JSON files, and turns them into data frames for training (or, bandit) trials, test trials, and catch trials.

# Libraries

```{r, message=FALSE}
library(jsonlite)
setwd("~/Documents/research/dependent-measures/bandit/analysis")
```

# Read in all the JSON strings

```{r comment=NA}
read.file <- function(filename) {
  con <- file(filename, "r", blocking = TRUE)
  lines <- paste(readLines(con, warn = FALSE), collapse = "\n")
  close(con)
  lines
}

#json.dir <- "../mturk/sandbox-results/"
json.dir <- "../follow-up-1/turk/production-results/"

json.filenames <- paste0(json.dir, list.files(json.dir))
json.strings <- Map(read.file, json.filenames)
```

# Convert JSON to a R data frame

Merge all the json strings together, as if they are in a big array, and convert it to an R data frame:

```{r comment=NA}
json.superstring <- paste("[",paste(json.strings, collapse = ","),"]")
assignments <- fromJSON( json.superstring )
```

## Subject information (incl. comments)

```{r}

subj.data <- cbind(data.frame(workerid=assignments$WorkerId,
                              duration =assignments$answers$time_in_minutes), 
                        assignments$answers$subject_information)

View(subj.data)
```

## Anonymize workerId

```{r}
# create "dictionary"
worker.list<-levels(subj.data$workerid)

# rewrite with anonymized IDs
subj.data$workerid<-as.factor(1:length(worker.list))

# example of retrieving workerId from anonymized number
worker.list[to.n(subj.data$workerid[3])]
# example of going from workerID to anonymized number
which(worker.list=="workerid")


write.csv(subj.data, '../data/bandit2_n80_subject_data_anonymized.csv')
```

# Trial data

```{r}
trial.data <- Map(function(id, subject.trial.data) { cbind(workerid = id, subject.trial.data) },
                  #assignments$WorkerId,
                  subj.data$workerid,
                  assignments$answers$trials)

is.bandit <- function(x) {
  return (x$trial_type[[1]]=='multi_trial')
}

is.elicit <- function(x) {
  return (x$trial_type[[1]]!='multi_trial')
}

strip.rownames <- function(x) {
  rownames(x) <- NULL
  x
}

trial.all <- strip.rownames(do.call(rbind, trial.data))

d.train <- filter(trial.all, trial_type=='multi_trial')
d.test <- filter(trial.all, trial=='prevalence')
d.catch <- filter(trial.all, substring(trial,1,5)=='catch')
write.csv(d.train, '../data/bandit2_n80_training_data_anonymized.csv')
write.csv(d.test, '../data/bandit2_n80_test_data_anonymized.csv')
write.csv(d.catch, '../data/bandit2_n80_catch_data_anonymized.csv')
```



