---
title: "bandit2"
author: "mht"
date: "March 16, 2015"
output: html_document
---

```{r, echo=FALSE, message=FALSE}
#library(MASS)
library(lme4)
source("C:/Users/Davis/Downloads/Ranalysis-master/Ranalysis-master/useful.R")
```

Herein lies the analysis for the first experiment of the bandit elicitation paradigm.

Subject data (incl. comments, strategies)
```{r init}
#setwd("../data/")
#setwd("D:/Git/Self-reported-Probability-matching/data")
d.subj<-read.csv('../data/bandit2_n80_subject_data_anonymized.csv')#,stringsAsFactors=F)
View(d.subj)
```

```{r}

d.train <- read.csv("../data//bandit2_n80_training_data_anonymized.csv")
View(d.train)


str(d.train)

d.train <- d.train %>%
  select(workerid,rt,bias_.,trial,result,ntrials,response,matched) %>%
  rename(bias=bias_.,
         trial.num=trial,
         marble=result) %>%
  mutate(bias = factor(bias),
         ntrials = factor(ntrials),
         workerid = factor(workerid))
  
str(d.train)
```

Subject-wise summarise data

```{r mutate}

# replace time-outs with 0s
d.train$marble<-replace(d.train$marble,which(d.train$marble==-1),0)

subj.stats<- d.train %>%
  #filter(marble!=-1) %>% # remove time-out trials; only matters for ""
  group_by(workerid, bias, ntrials) %>%
  summarise(rt_mean=mean(rt), 
            marble_mean=mean(marble),
            match_mean=mean(matched))

subj.history <- d.train %>%
  group_by(workerid, bias, ntrials) %>%
  mutate( match_cumul = cumsum(matched) / trial.num,
            marble_cumul = cumsum(marble) / trial.num)


```

## Analysis


We collected 80 subjects worth of data so we could focus on individial subjects

```{r probmatch}

ggplot(subj.history, aes(x=trial.num, y=match_cumul, color=bias))+
  geom_line()+
  geom_hline(aes(yintercept=to.n(bias)/100))+
  geom_hline(yintercept=0.5, linetype=2)+
  facet_wrap(~workerid)
```

Thoughts: 100 seems good. Some people get it at 50, but more at 100.

Davis: Is the difference between matching for 60 & 80 reduced when ntrials = 100?

```{r}
group.stats <- subj.stats %>%
  group_by(bias, ntrials) %>%
  summarise(match_mean_group = mean(match_mean),
            match_sterr_group = sem(match_mean)) %>%
  mutate(match_mean_group = match_mean_group-(to.n(bias)/100))
            
ggplot(group.stats, aes(x = ntrials, fill=bias, y= match_mean_group))+
  geom_bar(stat='identity', position=position_dodge(),width=0.3)+
  geom_errorbar(aes(ymin=match_mean_group-2*match_sterr_group, 
                    ymax = match_mean_group+2*match_sterr_group),
                position=position_dodge(),
                width = 0.3)


```

Ans: Possibly. Though all CIs overlap 0. Possibly the variance decreases with n = 100. The difference in matching between 60& 80 for the ntrials=50 might be slightly significant.


# Elicitation data

```{r}

d.test <- read.csv("../data/bandit2_n80_test_data_anonymized.csv")
View(d.test)

replace(d.test$response,which(d.test$ntrials==50),d.test$response*2)

double.count <- function(x,ntrials){
  if (to.n(ntrials)==50){
    count = x*2
    
  } else {
    count = x
  }
  return(count)
}

str(d.test)

d.test <- d.test %>%
  select(workerid,rt,bias_.,ntrials,response) %>%
  rename(bias=bias_.) %>%
  mutate(bias = factor(bias),
         ntrials = factor(ntrials),
         workerid = factor(workerid),
         response = (response/to.n(ntrials))*100)
  

test.stats<- d.test %>%
  group_by(bias, ntrials) %>%
  summarise(mean_response = mean(response),
            sterr = sem(response)) %>%
  mutate(mean_response = mean_response-to.n(bias))


ggplot(test.stats, aes(x = ntrials, fill=bias, y= mean_response))+
  geom_bar(stat='identity', position=position_dodge(),width=0.3)+
  geom_errorbar(aes(ymin=mean_response-2*sterr, 
                    ymax = mean_response+2*sterr),
                position=position_dodge(),
                width = 0.3)
```


```{r}
ggplot(d.test, aes(x=response, fill=bias))+
  geom_histogram(binwidth=1)+
  facet_grid(bias~ntrials)+
  xlim(0,100)

table(d.test$bias, d.test$ntrials)
```


Missing Trials?
=
```{r}
#This is odd. Two of the subjects didn't go through all 50 trials...
d.train %>% ungroup() %>%
  group_by(workerid) %>%
  summarise(N = length(rt)) %>%
  filter(!((N==50) || (N=100)))

```

Seemingly, we do have the right numbers of trials.

